---
title: "Week3 assignement"
author: "Amirhossein Vahidi"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: ioslides_presentation

---
## Investigating the influence of weight on mpg

```{r mtcars, echo=FALSE}
head(mtcars)
```
## Considering cycle and Power
- As you can see with increasing the weight the mpg increases
- Number of cycle and weight are correlated 

```{r library, include=FALSE}
library(plotly)
```
```{r plot1, echo=FALSE,message = FALSE,warning =FALSE}
plot_ly(mtcars, x = ~wt, y = ~mpg, type = "scatter", 
        color = ~factor(cyl), size = ~hp)
```

##  Considering displacement and Power
- Power and weight are not correlated 

```{r plot2, echo=FALSE,message = FALSE,warning =FALSE}
plot_ly(mtcars, x = ~wt, y = ~mpg, type = "scatter", color = ~hp, size = ~disp)
```

##  Considering transmission system 
- There is a correlation between transmission system  and weight
- Automatic transmission system has lower mpg
```{r plot3, echo=FALSE,message = FALSE,warning =FALSE}
plot_ly(mtcars, x = ~wt, y = ~mpg, type = "scatter", color = ~factor(am), size = ~hp)
```

## Thank you

